\subsection{Additional features}
Aside from the defined characteristics the module was expanded with
new functionalities in order to simplify some operations and allow 
other interesting capabilities.

\subsubsection{Masking/Predication}

Previously, I have stated my interest in adding to the processors 
predication, this feature is also compatible with a vector module
but is more commonly known as masking. The idea is simply to add
a boolean vector which determines weather the operation should modify
the result in the corresponding vector component. 

\medbreak
To keep the design modular, it is impossible to not overwrite the 
result register if this is not also passed to the module, but this 
idea was discarded in favor of passing the value of the first source
register. This is due to many times being the destination register also
the source one, and if needed the same result could be achieved with 
an additional instruction. 

\medbreak
The approach taken in the module is that the value of the mask vector 
must be set by a specific instruction and will keep this value until 
it is overwritten or the processor is reset. In the later case the value
will go back to the default one which is no mask.

\subsubsection{Swizzling}

The swizzling allows to reorder and duplicate the source vector components
to perform an operation using any combination. This is simply a multiplexor 
which picks which of the components is used in each byte operation. 

\medbreak
Same as in the mask case, the swizzling configuration is defined by an 
instruction and is constant until it's set again. In this case the default
configuration does not alter the original order of the register bytes.


